% \section*{Abstract}
% % A one-page summary of the project as a whole. This MUST be included for all projects.

\begin{abstract}
Neural Network is widely used in many fields.
And it has shown the ability to solve complex problems.
In addition, bisimulation is a very important logical concept.
This project is aiming to explore the capability of the neural network to understand this concept.
The project is divided into three parts.
In the first part, standard bisimulation algorithm was developed.
And one test case generator that can generate random graphs pairs with bisimulation flag is also developed base on the standard bisimulation.
In the second part, a simple neural network was developed to recognise bisimulation.
In the third part, a wide experiment and a deep experiment were done.
The wide experiment tests the performance of the neural network on the graphs of different density.
The result shows that the network performance well and show similarity in most of the cases.
It indicates the representativeness of the test cases produced by the developed random test case generator.
The deep experiment explores the limitation of the network by training the network in the large scale graphs pairs.
The result shows a good ability to understanding the bisimulation. 
However, for some larger scale graphs pairs, the network shows an unusually good performance.
It is speculated coursed by the small size of data set compare with the massive amount of possible graph pairs.
And more experiments still needed.
\end{abstract}