\section{Professional Issues}
\label{sec:profession}
% At least one page of discussion of how your project related to the codes of practice and conduct issued by the British Computer Society.
In this section the professional Issues base on the codes of practice and conduct issue by the British Computer Society will be discussed.

\subsubsection*{Technical Competence:}

At very first, trying to maintain the technical competence, all course provided by the university is taking. 
Further some extra online courses about the project like Machine Learning (see Section \ref{sec:learning}) and etc. has been taken during the project.
Also, before using the newly learned skill or some new design structure, it will be discussed during the regular meeting with the supervisor.
For example, the design scheme of the test case generator and the structure of the neural network were all discussed before actual implementation.

\subsubsection*{Public Interest:}
Data of this project did not involve any issue of public privacy, security and etc. directly.
All the data used here is self-generated abstract mathematical concepts. 
Any information related to intellectual property is annotated and used legitimately.
The softwares and libraries used either open source (e.g \texttt{TensorFlow}) or use free education version (e.g. \texttt{PyCharm}).

\subsubsection*{Duty to Relevant Authority:}
In the process of the project, the Relevant Authority's instruction is and will be respected and acted.
Section 9 of the Code of Practice on Assessment and University's Code of Practice is understood and acted honestly, ethically and professionally, during the whole process of the project.
Also, there is not any misrepresent information on the performance of any products involved in this project.

\subsubsection*{Duty to the Profession:}
Many pieces of literature relevant to the project had been read to maintain the specialism.
After the evaluation of this project, it is planned that the code of this project will be open-source under permission.
Thus, knowledge can be shared freely and support other researchers.



